The Hot Hand Fallacy in Call of Duty Search and Destroy

### 2022-08-30 paper/paper.Rmd
table 7

```{=tex}
\begin{equation}\label{eq:pwkri}
\hat{P}_0(\text{win} | k, r, i) = \hat{P}^{+|k,r,i}_0 := \begin{cases}
\frac{m - k}{r - k} & \text{team wins series}, i \neq r; \\
1 & \text{team wins series}, i = r; \\
\frac{s - m - k}{r - k} & \text{team loses series}, i \neq r, r > m + k; \\
0 & \text{team loses series}, i = r.
\end{cases}
\end{equation}
```
Again, we can apply a binomial test to evaluate the hypothesis that the expected proportion, $\hat{P}^{+|k,r,i}_0$, is equal to the observed proportion, $P^{+|k,r,i}$.

@@

  suppressMessages(
    cod_round_win_prop_after_z_with_probs <- cod_round_win_prop_after_z |> 
      group_by(win_series, n_rounds, ...) |> 
      mutate(
        total = sum(n),
        prop = n / total
      ) |> 
      ungroup() |> 
      select(n_rounds, win_round, win_series, ..., n, total, prop) |> 
      # filter(!win_round) |> 
      arrange(n_rounds, win_round, ...) |> 
      inner_join(
        probs_nx_k
      )
  )

  cod_round_win_prop_after_z_with_probs |> 
    mutate(
      notional_p_value = vectorized_binom_test(n, total, p = notional_prop)$p.value,
      ms_p_value = vectorized_binom_test(n, total, p = ms_prop)$p.value,
      notional_p_value_adj = notional_p_value |> p.adjust(method = 'BY')
    )
}

compute_probs_nx_k <- function(df, k) {
  df |> 
    mutate(
      is_valid = case_when(
        win_series ~ TRUE,
        (n_rounds - !!k - 6L) >= 0L ~ TRUE,
        TRUE ~ FALSE
      )
    ) |> 
    filter(is_valid) |> 
    select(-is_valid) |> 
    mutate(
      naive_prop = ifelse(win_series, 6L / n_rounds, (n_rounds - 6L) / n_rounds),
      notional_prop = (ifelse(win_series, 6L, n_rounds - 6L) - k) / (n_rounds - k),
      across(c(naive_prop, notional_prop), ~ifelse(win_round, .x, 1 - .x)),
      ms_prop = map2_dbl(
        n_rounds, naive_prop, 
        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
      ),
      across(
        ms_prop,
        ~ifelse(win_round, .x, naive_prop + (naive_prop - .x))
      ),
      across(
        ms_prop,
        ~ifelse(is.nan(ms_prop), naive_prop, .x)
      )
    )
}

summarize_cod_win_prop_after_k_wins <- function(k) {
  probs_nx_k <- crossing(
    n_rounds = 7L:11L,
    win_series = c(TRUE, FALSE),
    win_round = c(TRUE, FALSE)
  ) |> 
    compute_probs_nx_k(k)

  postprocess_round_streaks(
    k = k,
    probs_nx_k = probs_nx_k
  )
}

init_cod_round_win_prop_after_k_wins <- tibble(win_streak = 2L:5L) |>
  mutate(
    data = map(win_streak, summarize_cod_win_prop_after_k_wins)
  ) |>
  unnest(data)

cod_round_win_prop_after_k_wins <- init_cod_round_win_prop_after_k_wins |> 
  filter(win_round) |> 
  mutate(
    notional_p_value_adj = notional_p_value |> p.adjust(method = 'BY'),
    ms_p_value_adj = ms_p_value |> p.adjust(method = 'BY')
  )

@@

```{r}
#| label: cod_round_win_prop_after_k_wins_i_rounds
summarize_cod_win_prop_after_k_wins_i_rounds <- function(k) {
  probs_nx_k <- crossing(
    n_rounds = 7L:11L,
    round = 3L:11L,
    win_series = c(TRUE, FALSE),
    win_round = c(TRUE, FALSE)
  ) |> 
    filter(round >= (!!k + 1L), n_rounds > round) |> 
    compute_probs_nx_k(k)

@@

init_cod_round_win_prop_after_k_wins_i_rounds <- tibble(win_streak = 3L) |>
  mutate(
    data = map(win_streak, summarize_cod_win_prop_after_k_wins_i_rounds)
  ) |>
  unnest(data) |> 
  select(-starts_with('ms'))

cod_round_win_prop_after_k_wins_i_rounds <- init_cod_round_win_prop_after_k_wins_i_rounds |>
  group_by(win_streak, win_round, n_rounds, round) |> 
  mutate(
    total = sum(n),
    prop = n / total
  ) |> 
  ungroup() |> 
  mutate(
    notional_p_value = vectorized_binom_test(n, total, p = notional_prop)$p.value
  ) |> 
  filter(win_round) |> 
  mutate(
    notional_p_value_adj = notional_p_value |> p.adjust(method = 'BY')
  )

# ## example of why we needed to recalculate prop... prop and notional_prop should sum to 1, grouped by win_streak and win_round
init_cod_round_win_prop_after_k_wins_i_rounds |>
  filter(win_streak == 3, n_rounds == 11, round == 10)

cod_round_win_prop_after_k_wins_i_rounds |>
  filter(win_streak == 3, n_rounds == 11, round == 10)

# ## 5-3?
# cod_round_win_prop_after_k_wins_i_rounds |> 
#   filter(win_streak == 2) |> 
#   filter(n_rounds == 11, round == 11)
```

Table \ref{tbl:pw3ri} shows the observed and notional proportions of round wins immediately following streaks of three round wins when explicitly accounting for the round index, $i$.[^19]

@@

@@

\caption{For streaks of $k=3$ round wins in CoD SnD series ending in $r$ rounds, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ chances, given the index of the round, $i$, immediately following the streak. Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$. Table restricted to $r \in [10, 11]$, $i < r$, and $N^{k=3,r,i} \geq 10$.}

@@

10 & 7 & no & 2 & 13 & 15.4\% & 14.3\% \\ 
10 & 7 & yes & 11 & 13 & 84.6\% & 42.9\% \\ 
10 & 8 & no & 1 & 10 & 10.0\% & 14.3\% \\ 
10 & 8 & yes & 9 & 10 & 90.0\% & 42.9\% \\ 
11 & 5 & no & 9 & 13 & 69.2\% & 25.0\% \\ 
11 & 5 & yes & 4 & 13 & 30.8\% & 37.5\% \\ 
11 & 6 & no & 4 & 13 & 30.8\% & 25.0\% \\ 
11 & 6 & yes & 9 & 13 & 69.2\% & 37.5\% \\ 
11 & 7 & no & 3 & 10 & 30.0\% & 25.0\% \\ 
11 & 7 & yes & 7 & 10 & 70.0\% & 37.5\% \\ 
11 & 9 & no & 5 & 15 & 33.3\% & 25.0\% \\ 
11 & 9 & yes & 10 & 15 & 66.7\% & 37.5\% \\ 
11 & 10 & no & 5 & 10 & 50.0\% & 25.0\% \\ 
11 & 10 & yes & 5 & 10 & 50.0\% & 37.5\% \\

@@

In Table \ref{tbl:ww-sequences}, the observed and expected count of sequences respectively, are shown for sequence for which we can reject the Wald-Wolfowitz null hypothesis[^20] at a confidence level of $\alpha = 0.05$, for $r \in [6, 7, 8, 9, 10]$[^21]. In addition to the 14 sequences shown, there are 12 additional sequences for $r = 11$.

[^20]: Interestingly, we identify the same non-random sequences when using either $\phi = 0.575$ or $\phi = 0.5$.

[^21]: Since the normal method is invalid for sequences with only successes or failures, we use the exact method to evaluate (and reject) the null hypothesis for the Wald Wolfowitz runs test for $r = 6$.

@@

\caption{Sequences ($\zeta_j$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [6, 7, 8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively. The observed count, $N^{\zeta}_j$, and proportion, $P^{\zeta}_j$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta}_j$, and proportion, $\hat{P}^{\zeta}_j$. $\hat{N}^{\zeta}_j$ is scaled to the observed number of series played, hence its non-integer value.}

\centering
\begin{tabular}{rlrrrr}
\toprule
$r$ & $\zeta_j$ & $N^{\zeta}_j$ & $P^{\zeta}_j$ & $\hat{N}^{\zeta}_j$ & $\hat{P}^{\zeta}_j$ \\ 
\midrule
6 & + + + + + + & 40 & 4.7\% & 32.9 & 3.86\% \\
8 & - - + + + + + + & 4 & 0.47\% & 7.67 & 0.90\% \\ 
9 & - - - + + + + + + & 4 & 0.47\% & 3.75 & 0.44\% \\ 
10 & + + + + - - - - + + & 1 & 0.12\% & 2.39 & 0.28\% \\ 
10 & + - - - - + + + + + & 0 & 0.00\% & 2.04 & 0.24\% \\ 
10 & + - + - + + - + - + & 3 & 0.35\% & 2.04 & 0.24\% \\ 
10 & + + + - - - - + + + & 2 & 0.23\% & 2.04 & 0.24\% \\ 
10 & - - - - + + + + + + & 2 & 0.23\% & 1.79 & 0.21\% \\ 
10 & + - + - + - + + - + & 3 & 0.35\% & 1.70 & 0.20\% \\ 
10 & + - + + - + - + - + & 0 & 0.00\% & 1.70 & 0.20\% \\ 
10 & + + - - - - + + + + & 1 & 0.12\% & 1.19 & 0.14\% \\ 
10 & + - + - + - + - + + & 3 & 0.35\% & 1.11 & 0.13\% \\ 
10 & + + - + - + - + - + & 0 & 0.00\% & 1.11 & 0.13\% \\ 
10 & + + + + + - - - - + & 2 & 0.23\% & 1.02 & 0.12\% \\

>>>>

```{=tex}
\begin{equation}\label{eq:pwkri}
\hat{P}_0(\text{win} | k, r, i) = \hat{P}^{+|k,r,i}_0 := \begin{cases}
\frac{m-k-1}{r-k-1} & i < r-1; \\
\frac{1}{2} & i = r-1; \\
1 & \text{team wins series}, i = r; \\
0 & \text{team loses series}, i = r. \\
\end{cases}
\end{equation}
```
Again, we can apply a binomial test to evaluate the hypothesis that the expected proportion, $\hat{P}^{+|k,r,i}_0$, is equal to the observed proportion, $P^{+|k,r,i}$.

@@

  suppressMessages(
    cod_round_win_prop_after_z_with_probs <- cod_round_win_prop_after_z |> 
      group_by(win_series, n_rounds, ...) |> 
      mutate(
        total = sum(n),
        prop = n / total
      ) |> 
      ungroup() |> 
      select(n_rounds, win_round, win_series, round, n, total, prop) |> 
      arrange(n_rounds, win_round, ...) |> 
      inner_join(
        probs_nx_k
      )
  )

  cod_round_win_prop_after_z_with_probs |> 
    mutate(
      notional_p_value = vectorized_binom_test(n, total, p = notional_prop)$p.value
    )
}

filter_valid_n_rounds_combos <- function(df, k) {
  df |> 
    mutate(
      is_valid = case_when(
        win_series ~ TRUE,
        (n_rounds - !!k - 6L) >= 0L ~ TRUE,
        TRUE ~ FALSE
      )
    ) |> 
    filter(is_valid) |> 
    select(-is_valid)
}

summarize_cod_win_prop_after_k_wins <- function(k) {
  probs_nx_k <- crossing(
    n_rounds = 7L:11L,
    win_series = c(TRUE, FALSE),
    win_round = c(TRUE, FALSE)
  ) |> 
    filter_valid_n_rounds_combos(k) |> 
    mutate(
      naive_prop = ifelse(win_series, 6L / n_rounds, (n_rounds - 6L) / n_rounds),
      notional_prop = (ifelse(win_series, 6L, n_rounds - 6L) - k) / (n_rounds - k),
      across(c(naive_prop, notional_prop), ~ifelse(win_round, .x, 1 - .x)),
      ms_prop = map2_dbl(
        n_rounds, naive_prop, 
        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
      ),
      across(
        ms_prop,
        ~ifelse(win_round, .x, naive_prop + (naive_prop - .x))
      ),
      across(
        ms_prop,
        ~ifelse(is.nan(ms_prop), naive_prop, .x)
      )
    )

  postprocess_round_streaks(
    k = k,
    probs_nx_k = probs_nx_k
  ) |> 
    mutate(
      ms_p_value = vectorized_binom_test(n, total, p = ms_prop)$p.value
    )
}

cod_round_win_prop_after_k_wins <- tibble(win_streak = 2L:5L) |>
  mutate(
    data = map(win_streak, summarize_cod_win_prop_after_k_wins)
  ) |>
  unnest(data) |> 
  filter(win_round) |> 
  mutate(
    notional_p_value_adj = notional_p_value |> p.adjust(method = 'BY'),
    ms_p_value_adj = ms_p_value |> p.adjust(method = 'BY')
  )

@@

```{r}
#| label: cod_round_win_prop_after_k_wins_i_rounds
summarize_cod_win_prop_after_k_wins_i_rounds <- function(k) {
  probs_nx_k <- crossing(
    n_rounds = 7L:11L,
    round = (!!k):11L,
    win_series = c(TRUE, FALSE),
    win_round = c(TRUE, FALSE)
  ) |> 
    filter(round >= (!!k + 1L), n_rounds > round) |> 
    filter_valid_n_rounds_combos(k) |> 
    mutate(
      notional_prop = case_when(
        round == (n_rounds - 1L) ~ 0.5,
        round == n_rounds & win_series ~ 1,
        round == n_rounds & !win_series ~ 0,
        TRUE ~ (COD_WIN_THRESHOLD - !!k - 1) / (n_rounds - !!k - 1)
      ),
      across(notional_prop, ~ifelse(win_round, .x, 1 - .x))
    )

@@

cod_round_win_prop_after_k_wins_i_rounds <- tibble(win_streak = 2L:5L) |>
  mutate(
    data = map(win_streak, summarize_cod_win_prop_after_k_wins_i_rounds)
  ) |>
  unnest(data) |>
  filter(win_round) |> 
  group_by(win_streak) |> 
  mutate(
    notional_p_value_adj = notional_p_value |> p.adjust(method = 'BY')
  ) |> 
  ungroup()

cod_round_win_prop_after_k_wins_i_rounds |> 
  filter(notional_p_value < 0.05)
cod_round_win_prop_after_k_wins_i_rounds |> 
  filter(notional_p_value_adj < 0.05)
```

Table \ref{tbl:pw3ri} shows the observed and notional proportions of round wins---$P^{+|k=3,r,i}$ and $\hat{P}^{+|k=3,r,i}_0$ respectively---immediately following streaks of three round wins when explicitly accounting for the post-streak round index, $i$.[^19][^20] While some of the observed and notional proportions differ strongly, the BY-corrected $p$-values indicate that the null hypothesis cannot be rejected for any combination of $i$ and $r$ (including those not shown).[^21] The same is true for streaks of two, four, and five.

@@

[^20]: Some combinations of $r$ and $i$ are not shown in the table for brevity.

[^21]: There are combinations for which we could reject the null hypothesis if we did apply the BY correction, such as for $r = 10$ and $i = 9$.

@@

\caption{For streaks of $k=3$ round wins in CoD SnD series ending in $r$ rounds, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ chances, given the index of the round, $i$, immediately following the streak. Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$. Table restricted to $r \in [10, 11]$ and $r - 3 \leq i \leq r - 1$.}

@@

10 & 7 & no & 2 & 6 & 33.3\% & 33.3\% \\ 
10 & 7 & yes & 11 & 27 & 40.7\% & 33.3\% \\ 
10 & 8 & no & 1 & 13 & 7.7\% & 33.3\% \\ 
10 & 8 & yes & 9 & 24 & 37.5\% & 33.3\% \\ 
10 & 9 & no & 2 & 12 & 16.7\% & 50.0\% \\ 
10 & 9 & yes & 4 & 20 & 20.0\% & 50.0\% \\ 
11 & 8 & no & 2 & 17 & 11.8\% & 28.6\% \\ 
11 & 8 & yes & 3 & 19 & 15.8\% & 28.6\% \\ 
11 & 9 & no & 5 & 12 & 41.7\% & 28.6\% \\ 
11 & 9 & yes & 10 & 20 & 50.0\% & 28.6\% \\ 
11 & 10 & no & 5 & 14 & 35.7\% & 50.0\% \\ 
11 & 10 & yes & 5 & 22 & 22.7\% & 50.0\% \\

@@

In Table \ref{tbl:ww-sequences}, the observed and expected count of sequences respectively, are shown for sequence for which we can reject the Wald-Wolfowitz null hypothesis[^22] at a confidence level of $\alpha = 0.05$, for $r \in [6, 7, 8, 9, 10]$[^23]. In addition to the 14 sequences shown, there are 12 additional sequences for $r = 11$.[^24]

[^22]: Interestingly, we identify the same non-random sequences when using either $\phi = 0.575$ or $\phi = 0.5$.

[^23]: Since the normal method is invalid for sequences with only successes or failures, we use the exact method to evaluate (and reject) the null hypothesis for the Wald Wolfowitz runs test for $r = 6$.

[^24]: Non-random sequences for $r = 11$ excluded for brevity.

@@

\caption{Sequences ($\zeta_j$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [6, 7, 8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively. Additionally, the observed count, $N^{\zeta}_j$, and proportion, $P^{\zeta}_j$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta}_j$, and proportion, $\hat{P}^{\zeta}_j$. $\hat{N}^{\zeta}_j$ is scaled to the observed number of series played, hence its non-integer value.}

\centering
\begin{tabular}{rlrrrr}
\toprule
$r$ & $\zeta_j$ & $N^{\zeta}_j$ & $P^{\zeta}_j$ & $\hat{N}^{\zeta}_j$ & $\hat{P}^{\zeta}_j$ \\ 
\midrule
6 & + + + + + + & 40 & 4.69\% & 32.9 & 3.86\% \\
8 & - - + + + + + + & 4 & 0.47\% & 7.67 & 0.90\% \\ 
9 & - - - + + + + + + & 4 & 0.47\% & 3.75 & 0.44\% \\ 
10 & + + + + - - - - + + & 1 & 0.12\% & 2.39 & 0.28\% \\ 
10 & + - - - - + + + + + & 0 & 0.00\% & 2.04 & 0.24\% \\ 
10 & + - + - + + - + - + & 3 & 0.35\% & 2.04 & 0.24\% \\ 
10 & + + + - - - - + + + & 2 & 0.23\% & 2.04 & 0.24\% \\ 
10 & - - - - + + + + + + & 2 & 0.23\% & 1.79 & 0.21\% \\ 
10 & + - + - + - + + - + & 3 & 0.35\% & 1.70 & 0.20\% \\ 
10 & + - + + - + - + - + & 0 & 0.00\% & 1.70 & 0.20\% \\ 
10 & + + - - - - + + + + & 1 & 0.12\% & 1.19 & 0.14\% \\ 
10 & + - + - + - + - + + & 3 & 0.35\% & 1.11 & 0.13\% \\ 
10 & + + - + - + - + - + & 0 & 0.00\% & 1.11 & 0.13\% \\ 
10 & + + + + + - - - - + & 2 & 0.23\% & 1.02 & 0.12\% \\

### 2022-08-30 paper/paper.tex
table 7

\begin{equation}\label{eq:pwkri}
\hat{P}_0(\text{win} | k, r, i) = \hat{P}^{+|k,r,i}_0 := \begin{cases}
\frac{m - k}{r - k} & \text{team wins series}, i \neq r; \\
1 & \text{team wins series}, i = r; \\
\frac{s - m - k}{r - k} & \text{team loses series}, i \neq r, r > m + k; \\
0 & \text{team loses series}, i = r.
\end{cases}
\end{equation}

@@

Table \ref{tbl:pw3ri} shows the observed and notional proportions of
round wins immediately following streaks of three round wins when
explicitly accounting for the round index, \(i\).\footnote{We omit the
  MS proportions \(\hat{P}^{+|k=3,r,i}_{MS}\) since sample sizes are
  small and results may or may not be valid due to the questionable
  i.i.d assumption.}

@@

In Table \ref{tbl:ww-sequences}, the observed and expected count of
sequences respectively, are shown for sequence for which we can reject
the Wald-Wolfowitz null hypothesis\footnote{Interestingly, we identify
  the same non-random sequences when using either \(\phi = 0.575\) or
  \(\phi = 0.5\).} at a confidence level of \(\alpha = 0.05\), for
\(r \in [6, 7, 8, 9, 10]\)\footnote{Since the normal method is invalid
  for sequences with only successes or failures, we use the exact method
  to evaluate (and reject) the null hypothesis for the Wald Wolfowitz
  runs test for \(r = 6\).}. In addition to the 14 sequences shown,
there are 12 additional sequences for \(r = 11\).

>>>>

\begin{equation}\label{eq:pwkri}
\hat{P}_0(\text{win} | k, r, i) = \hat{P}^{+|k,r,i}_0 := \begin{cases}
\frac{m-k-1}{r-k-1} & i < r-1; \\
\frac{1}{2} & i = r-1; \\
1 & \text{team wins series}, i = r; \\
0 & \text{team loses series}, i = r. \\
\end{cases}
\end{equation}

@@

Table \ref{tbl:pw3ri} shows the observed and notional proportions of
round wins---\(P^{+|k=3,r,i}\) and \(\hat{P}^{+|k=3,r,i}_0\)
respectively---immediately following streaks of three round wins when
explicitly accounting for the post-streak round index,
\(i\).\footnote{We omit the MS proportions \(\hat{P}^{+|k=3,r,i}_{MS}\)
  since sample sizes are small and results may or may not be valid due
  to the questionable i.i.d assumption.}\footnote{Some combinations of
  \(r\) and \(i\) are not shown in the table for brevity.} While some of
the observed and notional proportions differ strongly, the BY-corrected
\(p\)-values indicate that the null hypothesis cannot be rejected for
any combination of \(i\) and \(r\) (including those not
shown).\footnote{There are combinations for which we could reject the
  null hypothesis if we did apply the BY correction, such as for
  \(r = 10\) and \(i = 9\).} The same is true for streaks of two, four,
and five.

@@

In Table \ref{tbl:ww-sequences}, the observed and expected count of
sequences respectively, are shown for sequence for which we can reject
the Wald-Wolfowitz null hypothesis\footnote{Interestingly, we identify
  the same non-random sequences when using either \(\phi = 0.575\) or
  \(\phi = 0.5\).} at a confidence level of \(\alpha = 0.05\), for
\(r \in [6, 7, 8, 9, 10]\)\footnote{Since the normal method is invalid
  for sequences with only successes or failures, we use the exact method
  to evaluate (and reject) the null hypothesis for the Wald Wolfowitz
  runs test for \(r = 6\).}. In addition to the 14 sequences shown,
there are 12 additional sequences for \(r = 11\).\footnote{Non-random
  sequences for \(r = 11\) excluded for brevity.}
